Examining background gene lists in clusterProfiler - RNA-seq example

### 2024-05-31 analysis/analyse_rnaseq2.Rmd
added fdr analysis

@@

This function fixes the problem with excluding un-annotated genes.

@@

  bgdf <- data.frame("background",bg)
  names(bgdf) <- c("term","gene")
  gs1 <- rbind(gs1,bgdf)

@@

@@

@@

>>>>

  gs1 <- gs1[which(gs1$gene %in% bg),]

@@

This function fixes the problem with not inlcuding sets for FDR correction.

@@

  gs1 <- gs1[which(gs1$gene %in% bg),]
  terms <- names(which(table(gs1$term)>5))
  gs1 <- gs1[gs1$term %in% terms,]

@@

  nsets <- length(which(table(gs1$term)>5))
  nres <- nrow(ora_up)
  diff <- nsets - nres
  pvals <- c(ora_up$pvalue,rep(1,diff))
  ora_up$p.adjust <- p.adjust(pvals,method="fdr")[1:nrow(ora_up)]

@@

  nsets <- length(which(table(gs1$term)>5))
  nres <- nrow(ora_dn)
  diff <- nsets - nres
  pvals <- c(ora_dn$pvalue,rep(1,diff))
  ora_dn$p.adjust <- p.adjust(pvals,method="fdr")[1:nrow(ora_dn)]

@@

ora_dat <- lapply(1:3, function(i) {
  j=params[i,1]
  k=params[i,2]
  bad <- orabad(d[[j]],gs[[k]])
  good <- oragood(d[[j]],gs[[k]])
  res <- compare_ora(bad,good)
  return(res)
} )
